Outline

### 2020-10-16 text/methods.Rmd
some edits from comments LV
last edits before sending to all coauthors

## 2. Bioenergetic modeling
\noindent We applied a series of bioenergetic models for each existing combination of species identity, body size, and sea surface temperature (n = 30668). The bioenergetic model framework integrates elements of metabolic theory, stoichiometry, and flexible elemental limitation [@Schiettekatte2020]. As such, this model is well suited for the application of a wide variety of fish species. The model relies on a set of input parameters including elements of metabolism, growth, and diet and body stoichiometry. We quantified the input parameters for all species through the integration of empirical data, data synthesis, and Bayesian phylogenetic models (See supplementary methods). The bioenergetic model then allows for the prediction of elemental fluxes mediated by individuals, including ingestion rate, excretion rates of N and P, and growth rate. Here, we focused on 5 key processes: N excretion rate (g N / day), P excretion rate (g P/day), production of body mass through growth (g C/day), herbivory, i.e. ingestion rate of macrophytes (g/day), and piscivory, i.e. ingestion rate of fishes (g/day). We summed the contribution of each individual to each process on the transect-level, to get community-level estimates, then dividing it by the surface area that was surveyed. Each process is thus expressed in dry mass per day per square meter. We note that N excretion, P excretion, and production include contributions of all fishes, whereas herbivory and piscivory are only carried out by a subset of the community, with respect to their trophic guild (@Parravicini2020).

@@

To assess the effect of biomass and sea surface temperature sst), we performed a Bayesian mixed effect regression of each log-transformed function for transect-scale observations ($y_j$):
<!-- \begin{equation} -->
	$$y_\textrm{j} \sim N(\mu_j, \sigma_j),$$
<!-- 	\label{modbiom1} -->
<!-- \end{equation}      -->

@@

\noindent We then assessed the covariation between functions, independent of biomass and sst. To do so, we first extracted the median residuals for each function per transect. In some transects, there were no piscivores or herbivores observed. In those cases, we did not include these transects in the analysis. To assess the covariation, we then quantified the correlations that exist among the different functions. To visualize the residuals per locality on a world map, we first grouped all transects per site by taking the median value for each process across multiple transect. We then grouped the sites again into localities by taking the median.

## 4. Effect of community structure on ecosystem functions 
\noindent To investigate the effect of the community structure accounting for the effect of standing biomass and sea surface temperature, we quantified a set of variables that characterize the community. These variables describe the size, age, and trophic distribution of the community, as these may all affect functions [@Schiettekatte2020]. Specifically, we took the 2.5%, 50% and 97.5% quantiles of the total length, immaturity, and trophic level of all individuals per transect. The total length is based on the visual estimation by divers. The immaturity is quantified using the following formula: 
<!-- \begin{equation} -->
	$$\textrm{immaturity}_\textrm{i} = \kappa (\textrm{l}_{\infty} - \textrm{l}_\textrm{i}),$$
<!-- 	\label{imm} -->
<!-- \end{equation} -->
where $\kappa$ is the species-specific growth rate parameter and $l_{\infty}$ is the species-specific asymptotic adult length, and $l_i$ is the total length of individual i. Essentially, this is the derivative of the Von Bertalanffy growth model for a certain length, and the higher this value is, the younger the individual. Finally, the trophic level was extracted from fishbase [@Froese2018]. Additionally, we quantified the transect-level species richness. 
For each log-transformed function we then fitted a Bayesian mixed-effect model with all 12 above-mentioned variables:

@@

## 5. Species dominance and contributions to functions
To investigate the role of each species for each function, we quantified the contribution of each species to each function for all transects as followed:
<!-- \begin{equation} -->
$$	\textrm{contribution}_{f,i,j} = \frac{\sum F_{f,i,j}}{\sum F_{f,j}},$$
<!-- 	\label{con} -->
<!-- \end{equation} -->
where i is a certain species, j is a transect, F is the value of function f.

@@

## 6. Vulnerability to fishing and climate change
For each species, we quantified two measures of vulnerability: vulnerability to climate change and vulnerability to fishing pressure [@Graham2011]. For species' vulnerability to climate change, we solely focus on their vulnerability to the loss of live corals. Vulnerability to climate change is related to diet specialization, habitat specialization, recruitment specialization for live coral and body size [@Graham2011]. Graham et al. (2011) [@Graham2011] developed a score for climate change vulnerability for 134 species. We used these scores to fit a Bayesian mixed effect predictive model that relates the vulnerability with the log-transformed maximum size of fish (extracted from Fishbase @Froese2018), the dependence on coral for food (3 categories: not dependent, facultative corallivore, and obligate corallivore), and dependence on coral for habitat (2 categories: dependent vs. not dependent). We also included a random effect for family. This model had a Bayesian R2 of 0.97. We then used this model to extrapolate the vulnerability measure to all 1110 species in our dataset. For species' vulnerability to fishing, we extracted the index from Cheung et al. (2005) @Cheung2005.
Then, we calculated vulnerability scores per function on the community level by averaging the species-level scores weighted by the contributions to function of species. Finally, we calculated proportions of communities with either high (upper quartile) or low (lower quartile) vulnerability for each function. We also report the proportion of communities that have high or low vulnerability scores for both climate change and fishing.

>>>>

## 2. Bioenergetic modeling
\noindent We applied a series of bioenergetic models for each existing combination of species identity, body size, and sea surface temperature (n = 30668). The bioenergetic model framework integrates elements of metabolic theory, stoichiometry, and flexible elemental limitation [@Schiettekatte2020]. As such, this model is well suited for the application of a wide variety of fish species. The model relies on a set of input parameters including elements of metabolism, growth, and diet and body stoichiometry. We quantified the input parameters for all species through the integration of empirical data, data synthesis, and Bayesian phylogenetic models (See supplementary methods). The bioenergetic model then allows for the prediction of elemental fluxes mediated by individuals, including ingestion rate, excretion rates of N and P, and growth rate. Here, we focused on 5 key processes: N excretion rate (g N / day), P excretion rate (g P/day), production of body mass through growth (g C/day), herbivory, i.e. ingestion rate of macrophytes (g/day), and piscivory, i.e. ingestion rate of fishes (g/day). We summed the contribution of each individual to each process on the transect-level, to get community-level estimates, then dividing it by the surface area that was surveyed. Each process is thus expressed in dry mass per day per square meter. We note that N excretion, P excretion, and production include contributions of all fishes, whereas herbivory and piscivory are only carried out by a subset of the community, with respect to their trophic guild [@Parravicini2020]. To reduce the occurrence of misclassification of herbivores and piscivores, we only categorized a species as a herbivore or piscivore if it had both the highest probability to be classified in that trophic group and this probability was more than 0.5, based on the probability scores of trophic guilds for a global fish species database [@Parravicini2020]. Further, as a comparison, we quantified herbivory and piscivory rates using two alternative trophic guild classifications based on expert opinion (Extended data figure 5). We can conclude that overall the herbivory and piscivory rates are very similar across trophic guild classifications, we are slightly conservative in piscivory rate estimations, and herbivory rates are almost equal to rates based on Siqueira et al. (2020) [@Siqueira2020], and exceed estimations based on Mouillot et al. (2014) [@Mouillot2014], which can be explained by the fact that this database classified many herbivores as omnivores. Thus, we opted to use the trophic classification by Parravicini et al. (2020), that defines trophic guilds based on empirical data using a quantitative, unbiased, and fully reproducible framework [@Parravicini2020].

@@

The standing stock biomass of communities is inevitably related to all functions because of the additive nature of the quantification and general metabolic theory. Furthermore, because of the known relationship between temperature and parameters related to growth and respiration, all functions are also positively correlated with temperature. To model the effect of biomass and sea surface temperature (sst), independent of other factors, we performed a Bayesian mixed effect regression of each log-transformed function for community-level observations ($y_j$):
<!-- \begin{equation} -->
	$$y_\textrm{j} \sim N(\mu_j, \sigma_j),$$
<!-- 	\label{modbiom1} -->
<!-- \end{equation}      -->

@@

\noindent We then assessed the covariation between functions, independent of biomass and sst. To do so, we first extracted the median residuals for each function per transect. In some transects, there were no piscivores or herbivores observed. In those cases, we did not include these transects in the analysis. We then quantified the correlations that exist among the different functions using these median residuals. Finally, for the purpose of visualizing the residual variation of functions per locality on a world map, we ran a supplemental model, similar to the model described above but including random effects both per site and locality. We then extracted and plotted the location effects, which can be interpreted as the average variation per locality.

## 4. Effect of community structure on ecosystem functions 
\noindent To investigate the effect of the community structure while still accounting for the effects of standing biomass and sea surface temperature, we quantified a set of variables that characterize the community. These variables describe the size, age, and trophic distribution of the community, as these may all affect functions [@Schiettekatte2020]. Specifically, we calculated the 2.5%, 50% and 97.5% quantiles of the total length, immaturity, and trophic level of all individuals per transect. The total length is based on the visual estimation by divers. The immaturity is quantified using the following formula: 
<!-- \begin{equation} -->
	$$\textrm{immaturity}_\textrm{i} = \kappa (\textrm{l}_{\infty} - \textrm{l}_\textrm{i}),$$
<!-- 	\label{imm} -->
<!-- \end{equation} -->
where $\kappa$ is the species-specific growth rate parameter and $l_{\infty}$ is the species-specific asymptotic adult length, and $l_i$ is the total length of individual i. Essentially, this is the derivative of the Von Bertalanffy growth model for a certain length, and the higher this value is, the younger the individual. Finally, the trophic level was extracted from fishbase [@Froese2018]. Additionally, we quantified the transect-level species richness. 
For each log-transformed function we then fitted a Bayesian mixed-effect model with all 12 above-mentioned variables:, after verifying that there are no strong correlations between variables (the highest correlation coefficient was 0.5, and 50% of the variable pair correlations varied between -0.1 and 0.2).

@@

## 5. Species dominance and contributions to functions
To investigate the role of species for each function, we quantified the contribution of each species to each function for all transects as followed:
<!-- \begin{equation} -->
$$	\textrm{contribution}_{f,i,j} = \frac{\sum F_{f,i,j}}{\sum F_{f,j}},$$
<!-- 	\label{con} -->
<!-- \end{equation} -->
where i is a certain species, j is a transect, F is the value of function f.

@@

## 6. Vulnerability to fishing and climate change
For each species, we quantified two measures of vulnerability: vulnerability to climate change and vulnerability to fishing pressure [@Graham2011]. For species' vulnerability to climate change, we solely focus on their vulnerability to the loss of live corals. Vulnerability to climate change induced coral loss is related to diet specialization, habitat specialization for live coral and body size [@Graham2011]. Graham et al. (2011) [@Graham2011] developed a score for climate change vulnerability for 134 species. We used these scores to fit a Bayesian mixed effect predictive model that relates the vulnerability with the log-transformed maximum size of fish (extracted from Fishbase @Froese2018), the dependence on coral for food (3 categories: not dependent, facultative corallivore, and obligate corallivore), and dependence on coral for habitat (2 categories: dependent vs. not dependent) [@Coker2014; @Cole2008]. We also included a random effect for family. To verify the fit of the model we inspected the posterior predictive plot, which indicated a good fit. Further, the model had a Bayesian R2 of 0.97. We thus used this model to extrapolate the vulnerability measure to all 1110 species in our dataset. For species' vulnerability to fishing, we extracted the index from Cheung et al. (2005) [@Cheung2005].
Next, we calculated vulnerability scores per function on the community level by averaging the species-level scores weighted by the contributions to function of species. We also calculated community-level vulnerability scores based on biomass contributions as a comparison. Finally, we calculated the proportions of communities that had a higher vulnerability score of functions, compared to the vulnerability score based on biomass alone. In other words, we quantified the proportions of communities that have an increased functional vulnerability.

### 2020-10-16 text/suppl_methods.Rmd
last edits before sending to all coauthors

We extracted the data for $k_{max}$ from Morais et al. (2018) @Morais2018 and filtered out only the species of our species list. As the Lenth-Frequency method consistently overestimates kmax, we omitted the $k_{max}$ estimates coming from this method. In total, this selection process resulted in 439 observations of kmax for different species and temperatures.

Further, we collected additional otolith data, including measurements of fishes from five Polynesian islands. 
We collected data across four archipelagos, including six distinct islands: Moorea and Manuae (Society Islands), Hao and Mataiva (Tuamotus), Mangareva (Gambiers), and Nuku Hiva (Marquesas) between 2014 and 2018. All fishes were collected in the lagoon and/or outer slope, depending on the accessibility of the respective habitats.

@@

## 2 Body stoichiometry    
### 2.1 Data collection    
\noindent 1633 individuals of 108 species and 25 families were collected between 2015 and 2017 in Moorea, the Caribbean, and Palmyra. Their gut contents were removed, and the whole body was freeze-dried and ground to powder with a Precellys homogenizer. $Q_\textrm{k}$ (\%) were then measured in the lab using standard methods. Ground samples were analysed for \%C and \%N content using a CHN Carlo-Erba elemental analyzer (NA1500) for \%P using dry oxidation-acid hydrolysis extraction followed by a colorimetric analysis [@Allen1974]. Elemental content was calculated based on dry mass.

@@

## 3 Diet stoichiometry    
### 3.1 Data collection 
\noindent We collected 571 adult individuals of 51 species between 2018 and 2019 in Mo'orea and Tetiaroa, and Mangareva, three Polynesian islands. We extracted the stomach content and stored it in a 2ml tube. After freezing the samples, we dry-froze all samples for at least 24 hours, and ground to powder. Then, samples were sent to the lab for CNP content analysis using similar methods as for the fish body stoichiometry.

>>>>

We extracted the data for $k_{max}$ from Morais et al. (2018) [@Morais2018] and filtered out only the species of our species list. As the Lenth-Frequency method consistently overestimates kmax, we omitted the $k_{max}$ estimates coming from this method. In total, this selection process resulted in 439 observations of kmax for different species and temperatures.

Further, we collected additional otolith data, including measurements of fishes from five Polynesian islands. 
We collected data across four archipelagos, including six distinct islands: Mo'orea and Manuae (Society Islands), Hao and Mataiva (Tuamotus), Mangareva (Gambiers), and Nuku Hiva (Marquesas) between 2014 and 2018. All fishes were collected in the lagoon and/or outer slope, depending on the accessibility of the respective habitats.

@@

## 2 Body stoichiometry    
### 2.1 Data collection    
\noindent 1633 individuals of 108 species and 25 families were collected between 2015 and 2017 in Mo'orea, the Caribbean, and Palmyra. Their gut contents were removed, and the whole body was freeze-dried and ground to powder with a Precellys homogenizer. $Q_\textrm{k}$ (\%) were then measured in the lab using standard methods. Ground samples were analysed for \%C and \%N content using a CHN Carlo-Erba elemental analyzer (NA1500) for \%P using dry oxidation-acid hydrolysis extraction followed by a colorimetric analysis [@Allen1974]. Elemental content was calculated based on dry mass.

@@

## 3 Diet     
### 3.1 Data collection 
\noindent We collected 571 adult individuals of 51 species between 2018 and 2019 in Mo'orea and Tetiaroa, and Mangareva, three Polynesian islands. We extracted the stomach content and stored it in a 2ml tube. After freezing the samples, we dry-froze all samples for at least 24 hours, and ground to powder. Then, samples were sent to the lab for CNP content analysis using similar methods as for the fish body stoichiometry.
